Long-Term Reproducibility through Replication:\\ the ReScience Initiative

### 2017-06-09 draft.tex
Fix typo in link

Performing a replication is a daunting task that is traditionally hardly or not
at all rewarded. Nevertheless, some people are actually willing to replicate
computational research. The motivations for doing so are very diverse (see Box 1). Students may want familiarize themselves with
a specific scientific domain, and acquire relevant practical experience by replicating important published work. Senior researchers may critically
need a specific piece of code for a research project and therefore re-implement a published computational method. If these people write a brand new
open source implementation of already published research, chances are that this new
implementation may be of great interest for other people as well, including
the original authors. The question is where to publish such a replication. To the
best of our knowledge, no major journal accepts publishing replications in computational science. This has been the main motivation for the
creation of the ReScience journal (\url{rescience.github.io}) by Konrad Hinsen
and Nicolas Rougier in 2015.\\

>>>>

Performing a replication is a daunting task that is traditionally hardly or not
at all rewarded. Nevertheless, some people are actually willing to replicate
computational research. The motivations for doing so are very diverse (see Box 1). Students may want familiarize themselves with
a specific scientific domain, and acquire relevant practical experience by replicating important published work. Senior researchers may critically
need a specific piece of code for a research project and therefore re-implement a published computational method. If these people write a brand new
open source implementation of already published research, chances are that this new
implementation may be of great interest for other people as well, including
the original authors. The question is where to publish such a replication. To the
best of our knowledge, no major journal accepts publishing replications in computational science. This has been the main motivation for the
creation of the ReScience journal (\href{https://rescience.github.io}{rescience.github.io}) by Konrad Hinsen and Nicolas P. Rougier in September 2015.\\
